\documentclass[10pt]{article}\usepackage{html}\begin{document}
\title{System Administration:\\Week 6 Lab}
\maketitle
\section{Logs}
\begin{enumerate}
\item Take a look at your Apache logs which logs the ip address which tried to acess you server, date and time, and other useful information and describe its format.  
\item Do you see anything suspicous in the logs, like somebody trying to compromise your server.
\item {\bf wget} the file \htmladdnormallink{http://pileup.ocf.berkeley.edu:11680/access.log.1}{http://pileup.ocf.berkeley.edu:11680/access.log.1} then store it somewhere and describe what you see. Hint: the stuff is not legit.
 \end{enumerate}
\section{Shell Scripting}
\begin{enumerate}
\item Write a script that will calculate the difference between two numbers. Hint: {\bf expr} could do mathematical evaluations. Alternatively you could use {\bf bc}.
\item Write a script that will output and store the difference between a file foo.1 and file foo.2 into foo.diff. Create some dummy files and test it. Hint: sed -e 's/foo/bar/g' would replace every occurance of foo with bar.
\item Challenge Write a shell script in bash that will print out an 8 x 8 chessboard on the screen. Hint: echo -e -n "$\backslash$033[40m" prints a white squre while echo -e -n "$\backslash$033[47m" prints a black square (in bash).
\end{enumerate}

\section{Cron jobs}
Pick one of the scripts and create a cron job for it to be executed in 5 minutes. How did create the job and what did you put inside the file? It will probably be easiest for you to use your root account on pileup to complete this.

\section{Submission}
As always....






\end{document}
